\documentclass[letterpaper,10pt]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{xcolor}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{empty}
\pdfgentounicode=1
\urlstyle{same}
\raggedright
\raggedbottom
\setlength{\tabcolsep}{0in}

% Margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.6in}
\addtolength{\textwidth}{1.2in}
\addtolength{\topmargin}{-0.7in}
\addtolength{\textheight}{1.35in}

% Section formatting
\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

% Custom commands
\newcommand{\resumeItem}[1]{
  \item \small{#1}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small #3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-8pt}
}

\newcommand{\resumeProjectHeading}[2]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \small #1 & #2 \\
    \end{tabular*}\vspace{-8pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in,label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.18in,itemsep=2pt,topsep=2pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-6pt}}

\begin{document}

\begin{center}
    \textbf{\Huge Zachary Gameiro} \\ \vspace{3pt}
    \small Burnaby, BC \,|\, (780) 340-9772 \,|\, \href{mailto:zachary_gameiro@sfu.ca}{zachary\_gameiro@sfu.ca} \,|\, 
    \href{https://www.linkedin.com/in/zachary-gameiro/}{linkedin.com/in/zachary-gameiro} \,|\, 
    \href{https://github.com/zacharydagameiro}{github.com/zacharydagameiro}
\end{center}

\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Simon Fraser University}{Burnaby, BC}
    {B.Sc., Joint Major in Computing Science and Biochemistry/Microbiology}{Expected May 2027}
\resumeSubHeadingListEnd

\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
    \textbf{Languages:} Python, C/C++, JavaScript, SQL, TI-BASIC \\
    \textbf{Frameworks \& Tools:} React, React Native, Node.js/Express, Git, Docker, Linux, Google Cloud Run, Firebase, Supabase, AWS \\
    \textbf{ML / Data:} PyTorch, PaddleOCR, HDBSCAN, DBSCAN, OCR pipelines, graph embeddings \\
    \textbf{Hardware:} Arduino, RF modules, embedded systems, soldering
  }}
\end{itemize}

\section{Projects}
\resumeSubHeadingListStart

  \resumeProjectHeading
    {\textbf{Receipt OCR to Structured Transaction Pipeline} $|$ \emph{Python, PaddleOCR, Docker, Cloud Run, LLM}}{2025}
    \resumeItemListStart
      \resumeItem{Built a two-stage receipt ingestion pipeline that converts receipt images into validated transaction JSON for merchant, date, totals, tax, and line items.}
      \resumeItem{Replaced the earlier multimodal-LLM OCR path with self-hosted PaddleOCR on Google Cloud Run, improving OCR throughput by about 200\% while reducing external API dependence.}
      \resumeItem{Used OCR bounding boxes to reconstruct layout-aware text and added schema-first normalization so downstream parsing produced more consistent records.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Embedded Wireless Messaging on TI-84 Calculators} $|$ \emph{Arduino, C/C++, TI-BASIC, nRF24L01}}{2020}
    \resumeItemListStart
      \resumeItem{Designed and assembled a wireless messaging system by integrating an Arduino Nano and RF transceiver inside TI-84 calculators.}
      \resumeItem{Reverse-engineered the TI-84 link interface and built Arduino firmware plus a TI-BASIC chat client for bidirectional communication.}
      \resumeItem{Debugged timing, signal, and power issues to achieve stable wireless messaging at roughly 30 feet.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Auto Sales PDF Automator} $|$ \emph{Python, PDF Processing, Validation}}{2025}
    \resumeItemListStart
      \resumeItem{Automated dealership paperwork generation by mapping structured customer and vehicle data into standardized PDF document templates.}
      \resumeItem{Implemented validation and normalization for required fields, dates, pricing, and input cleanup to reduce incomplete or inconsistent submissions.}
      \resumeItem{Collapsed repetitive multi-form entry into a single workflow, reducing redundant data entry and review overhead for staff.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{MIRO-Based SMLM Clustering Pipeline} $|$ \emph{Python, PyTorch, MIRO, HDBSCAN}}{2025}
    \resumeItemListStart
      \resumeItem{Built a clustering pipeline for single-molecule localization microscopy data using MIRO-based graph embeddings and density-based clustering.}
      \resumeItem{Reproduced and trained MIRO on custom localization data using mutual k-nearest-neighbor graphs.}
      \resumeItem{Applied DBSCAN/HDBSCAN to learned embeddings to identify molecular structures and generate reconstruction outputs.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

\section{Experience}
\resumeSubHeadingListStart

  \resumeSubheading
    {BCLDB}{BC, Canada}
    {Retail Associate}{June 2025 -- Present}
    \resumeItemListStart
      \resumeItem{Handle regulated products, customer verification, and inventory workflows under strict compliance requirements.}
      \resumeItem{Maintain accuracy in cash handling and front-line operations during high-volume shifts.}
    \resumeItemListEnd

  \resumeSubheading
    {Sherwood Park Toyota}{Sherwood Park, AB}
    {Sales Associate}{Summer 2025}
    \resumeItemListStart
      \resumeItem{Managed online sales inquiries and customer correspondence in a high-volume dealership environment.}
      \resumeItem{Executed customer-facing sales and contract workflows with accuracy under time pressure.}
    \resumeItemListEnd

  \resumeSubheading
    {Various Sites}{Canada}
    {Construction Labourer}{Summers 2020 -- 2024}
    \resumeItemListStart
      \resumeItem{Worked in safety-critical crews performing scaffolding, concrete, and site setup across changing jobsite conditions.}
      \resumeItem{Built reliability and teamwork under physical workloads, shifting constraints, and tight schedules.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}
